---
title: "HW3"
author: "Yuyu Fan"
date: "10/29/2019"
output:
  pdf_document: default
---

  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Question 1
## Ch.2  problem 4
```{r}
sample1975 <-c(17.74, 12.17, 12.22, 13.89, 16.47,
               15.88, 16.10,16.74, 17.54, 17.43,
               14.57, 12.90, 12.81, 14.95, 16.25,
               17.13, 14.46, 14.20,16.90,11.34,
               12.57, 13.15, 16.53, 13.60, 13.34,
               13.67, 14.23, 15.81, 16.63, 11.40,
               14.94,13.66, 9.79, 13.08, 14.57,
               14.93, 14.01, 14.43, 16.35, 15.65,
               11.52, 17.46, 14.67, 15.92, 16.02,
               13.46, 13.70, 14.98, 14.57,15.72)
hist(sample1975)
mean(sample1975)
sd(sample1975)

sample1985 <-c(24.57, 24.79, 22.21, 25.84, 25.35,
               22.19, 24.37, 21.32, 22.74, 23.38,
               25.10, 28.03, 29.09, 29.34, 24.41,
               25.12, 25.27, 27.46, 27.65, 27.95,
               21.67, 22.15, 24.36, 26.32, 24.05,
               28.27, 26.57, 26.10, 24.35, 30.04,
               25.18, 27.42, 24.50, 23.21, 25.10,
               23.59, 26.98, 22.64, 25.27, 25.84,
               27.18, 24.69, 26.35, 23.05, 23.37,
               25.46, 28.84, 22.14, 25.42, 21.76)
hist(sample1985)
mean(sample1985) ##there is an increase in the average values
sd(sample1985)
```
## comment on interesting aspect
## both the histogram plots appear to be normal distribution


## a list of questions
##  a) is there a siginificant difference of average between these two samples?
##     H0: mean(sample1975) == mean(sample1985)
##     alternative hypothesis: true difference in means is not equal to 0
##      1. as we don't know the population variance
##      2. and we have a fair large sample size that n1 and n2 both equal to 50
##      so we will conduct t.test with significance level 0.05
         
```{r}
 t.test(sample1975,sample1985)  
```

##     as we get a rather small p-value < 2.2e-16,
##     that we are confident to reject the null hypothesis, and accepct the alternative hypothesis

## b)  does the increase in the mean brought by the time changes?
##     plenty of other factors may cause this change, and we will need more data and variables to make a better intepretation


## Ch.2   problem 10
# (a) #
```{r}
random_bolts_sample <-rnorm(397,mean=3.06,sd=0.03)
mean(random_bolts_sample)
sd(random_bolts_sample)
n1 <- length(random_bolts_sample[random_bolts_sample<2.9])
n2 <- length(random_bolts_sample[random_bolts_sample>3.1])
n1
n2
```

conlusion: so n1= 0 bolts are found too shoryt, and n2=34 bolts are found too long

# (b) #
assumptions: 50 bolts are drawn randomly and sample means follow a normal distribution
```{r}
n1=12
n2=12
p1=n1/50
p2=n2/50
z2=qnorm(p2,mean=0,sd=1) #caculate z-value under standard normal distribution
z1=-z2
z1
z2
sd= (3.1-3)/0.7063026
```

z1=-0.7063026= (2.9-mean)/sd
z2= 0.7063026= (3.1-mean)/sd
conlusion: mean= 3, sd= 0.1415824

## Ch.2   problem 13
## (a)
```{r}
##theoritical probability
P1= 1/3
P1
n=6

p0=pbinom(0,6,1/3)
p1=pbinom(1,6,1/3)-pbinom(0,6,1/3)
p2=pbinom(2,6,1/3)-pbinom(1,6,1/3)
p3=pbinom(3,6,1/3)-pbinom(2,6,1/3)
p4=pbinom(4,6,1/3)-pbinom(3,6,1/3)
p5=pbinom(5,6,1/3)-pbinom(4,6,1/3)
p6=pbinom(6,6,1/3)-pbinom(5,6,1/3)

prob1 <-c(p0,p1,p2,p3,p4,p5,p6)
prob1


success_of_6 <-c(0,1,2,3,4,5,6)
freq1<-prob1*64
freq1

##theoritical mean
mean1=sum(t(success_of_6)*(freq1))/64
mean1

## theoritical variance
var1= (sum(t(success_of_6)^2*(freq1))-64*(mean1^2))/63
var1= n*P1*(1-P1)
var1
```

##(b)
```{r}
success_of_6 <-c(0,1,2,3,4,5,6)
freq2<-c(0,4,19,15,17,7,2)

r1=rep(1,4)
r2=rep(2,19)
r3=rep(3,15)
r4=rep(4,17)
r5=rep(5,7)
r6=rep(6,2)
r=c(r1,r2,r3,r4,r5,r6)
##empirical probability
P2 = sum(r)/(64*6)
P2

##empirical mean and variance
mean2=mean(r)
mean2

var2= var(r)
var2
```

# (c) #
```{r}
## test the mean
t.test(r,mu=2)
```

## p-value is as small as 2.942e-10, so we are confident to reject the null hypothesis
##  the mean of the sample is not equal to 2

```{r}
## test the variance
library(EnvStats)
varTest(r,sigma.squared = var1)
```

## p-value is as large as 0.3942, so we don't have enough confidence to reject the null hypothesis
## we are confident to say that the variance of the sample have its theoretical value


# (d) # 
## expected frequencies in the seven cells of the table 
```{r}
freq3 <- round(freq1)
sum(freq3)
freq3
```

## Question 2
## Ch.3  problem 2
```{r}
data <-matrix(c(9,10,9,8,9,8,8,8,7,6,9,10,11,9,10,11,
                         11,11,11,10,11,12,13,12,13,12,14,15,14,12,13,13,
                         12,13,13,13,13,13,10,8,9,8,6,7,7,6,5,6,
                         5,6,4,5,4,4,2,4,5,4,5,6,5,5,6,5,
                         6,7,8,8,8,7,9,10,9,10,9,8,9,8,7,7,
                         8,7,7,7,8,8,8,8,7,6,5,6,5,6,7,6,
                         6,5,6,6,5,4,3,4,5,5,6,5,6,7,6,5)
                        )

n1<-0
diff_sample= (3+4-8-6)/2
diff_sample

diff = rep(0,109)

for (k in 1:109){
  diff[k]=(data[k+2]+data[k+3]-data[k+1]-data[k])/2
  if (diff[k] < (-3.5)) {
  n1<-n1+1
  }
  
}
pvalue = n1/109
pvalue


```
Conclusion:  reject null hypothesis.
          p-value is as small as 0.009174312, only 1 out of the 109 differences are as great as -3.5. So we reject the null hypothesis and conclude that  S-142 works

## Ch.3  Problem 4
```{r}
brandA <- c(2,4,2,1,9,9,2,2)
brandB <- c(8,3,5,3,7,7,4)
t.test(brandA,brandB)
```

Conclusion:  p- value is as large as 0.3316, t is smaller than 2.179, so we don't have enough confidence to rejecet the null hypothesis
 there is no significant difference between these two beers
 
## preferred assignment: assign both beers A and B to each judge to taste and rate
## Purpose: Compare two brands of beers A and B 
## Treatment: Beer A and B
## Experiment units: 15 judges
## Randomization: for the sequence to taste beer A or B, decided by flipping a coin
## response: rate of beer's taste
## conduct a paired test of the experiement response

## perform a test based on a randomization distribution
```{r}
avg<-mean(brandB)-mean(brandA)
n1<-0
a=set.seed(4)
y1<-c(2,4,2,1,9,9,2,2,8,3,5,3,7,7,4)
h1<-NULL
c1<-c(rep("A",8), rep("B",7))
for (k in 1:10000){
  c2<-sample(c1)
  x1<-y1[c2=="A"]; x2<-y1[c2=="B"]
  m1<-mean(x1); m2<-mean(x2)
  d1<-m2-m1
  h1<-c(h1,d1)
  if (d1>=avg)n1<-n1+1
}
n1
p1<-n1/10000 
p1
##plot the histogram of differences
hist(h1)
```
Conclusion: since the p-value is as large as 0.1916, that we don't reject the null hypothesis based on the test

## Ch.3  problem 8
```{r}
TubeA <-c(1.176,1.230,1.146, 1.672,0.954, 1.079, 1.204)
TubeB <-c(1.279, 1.000, 1.146, 1.176, 0.699, 1.114, 1.114)
## paired ttest
t.test(TubeA,TubeB, paired=TRUE)
```

 since the p-value is 0.1409,and t = 1.6956 at 95% confidence level, we can't reject the null hypothesis
 there is no significicant difference between plate current readings of cpmpartment A and B
```{r}
## perform a test based on a randomization distribution
N<-0
d<-TubeA-TubeB
n<-length(d)
dm<-mean(d)
N<-10000
D<-rep(0,N)
for (i in 1:N){
  C<-sample(c(-1,1),n, replace=TRUE)
  D[i]<-mean(C*d)
}
a<-sum(abs(D)>=abs(dm))
p<-a/N
p
##plot the histogram of differences
hist(D)

```
 Conclusion: since the p-value is as large as 0.1849, that we don't reject the null hypothesis based on the test
             there is no siginificant difference between plate current readings of cpmpartment A and B
             

## Question 3
## Ch.3  problem 21
```{r}
NoTherapy = c(24,25,12)
Group=c(10,13,20)
Individual=c(41,32,9)
recidivism= cbind(NoTherapy,Group,Individual)
recidivism
```

assumption: a) samples are drawn randomly
            b) oberavtions are mutually exclusive
            c) errors are normally distributed
H0:p1=p2=p3
H1: at least one of the equations are not valid
```{r}
chisq.test(recidivism)
```

conclusion: Reject the null hypothesis
   the p-value is small enough, so we are confident to reject the null hypothesis. 
   The level of treatment will have an impact on recidivism.


